---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

##### **Chapter 4**

###### **4.1**

* Coding basics
    + We can do simple math equations in R
    + We can also assign variables in R with the <- operator or the = operator
    
###### **4.2**

* Naming
    + You can coose to name objects in different ways
        + name_one, name.one, NameOne are some examples
        + You can choose a way thats good for you and **stay consistent**
    + We can call and inspect objects by typing them in to the console
        + Be sure to use proper spelling and case sensitive
        + R will auto fill your objects while you're typing them
        
###### **4.3**

* Calling Functions
    + Basic function call: function.name(arg1 = value, arg2 = value...)
    + R will auto fill closing parenthesis and quotes while you're typing
        + If there isn't a closing parenthesis or quote, a **+** will appear in the console
    + If you want to auto print an object with an assignment put oarenthesis arounf the whole thing 
        + Example: **(object.name <- value)**
    + You can see all objects and functions under the "Envitonment" tab in the top left section of R Studio
    
###### **4.4**

Practice
1.
```{r 4.4 1}
my_variable <- 10
my_varıable
# The dot above the i is missing
my_variable
```
2. 
```{r 4.4 2}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8) # filter is spelled wrong and == is needed
filter(mpg, cyl == 8)
filter(diamond, carat > 3) # diamond data was not inputted
```
3. 
* Press alt+shift+k
    + this will bring up a shortcut menu
    

##### **Chapter 6**

###### **6.1**  

* Running Code 
    + If you type code into the script or code chunk, **ctrl+enter** will run the line you are on and move the cursor to the next line
        + You can run the entire script by using **ctrl+shift+s**
    + Always include the packages you use in your code with library(package.name)
    + Never add install.packages(package.name) because that will mess with the settings on other people's pc
    
###### **6.2**  

* Diagnostics
    + The script will show errors in code with squggle lines under code or a red X at the beginning of the line
        + You can hover over the X to see what errors are in that line
    + Script will put a yellow caution sign at the beginning of a line to warn against potential errors
    
###### **6.3** 

Practice
* Go to R Studio twitter
* Other errors R could throw


##### **Chapter 8**

###### **8.1** 

* What is real?
    + Your R script is "real"
    + It is not good practice to save your workspace.
    + Here is a shortcut to use instead of saving the workspace:
        + Press Cmd/Ctrl + Shift + F10 to restart RStudio.
        + Press Cmd/Ctrl + Shift + S to rerun the current script.
        
###### **8.2**   

* Where does your analysis live?
    + You should now be sorting your scripts into properly organized directories instead of the default ones
    
###### **8.3** 

* Paths and Directories
    + Make sure you are using the proper slashes. Some use / while others use \
    
###### **8.4** 

* Projects
    + Projects will keep all files associated with it in an organized place
    + When creating a new project make sure you save it in the proper directory for easy access later











